---
title: "Marginal effects visualization with ggplot2"
output: github_document
---

This package overrides plotting functions from the `margins` `R` package in order to produce `ggplot2` objects. This makes it much easier for users to customize the look of their marginal effects and predicted probabilities plots.

To install this package, execute the following commands:

```{r, eval = FALSE}
library(remotes)
install_github('vincentarelbundock/marginsplot')
```

To use the package, you need to load `marginsplot` **after** `margins`, to ensure that the new plotting functions take precedence. For example:

```{r}
library(margins)
library(marginsplot)
mod <- lm(hp ~ wt*drat, data = mtcars)
cplot(mod, dx = 'drat', x = 'wt')
```

Alternatively, you could explicitly prioritize `marginsplot` using the `conflicted` package:

```{r}
library(conflicted)
conflict_prefer('cplot', 'marginsplot')
conflict_prefer('plot', 'marginsplot')
```

The next section is a modified version of the `margins` README, which shows how to customize the output of `marginsplot`.

# Modified `margins` README

## Visualization

The package implements several useful additional features for summarizing model objects, including:

 - A `plot()` method for the new "margins" class that ports Stata's `marginsplot` command.
 - A plotting function `cplot()` to provide the commonly needed visual summaries of predictions or average marginal effects conditional on a covariate.
 - A `persp()` method for "lm", "glm", and "loess" objects to provide three-dimensional representations of response surfaces or marginal effects over two covariates.
 - An `image()` method for the same that produces flat, two-dimensional heatmap-style representations of `persp()`-type plots.
 
`plot()` and `cplot()` return `ggplot2` objects, which can be further customized using themes and other `ggplot2` options.

### Marginal effects plots

Using the `plot()` method yields an aesthetically similar result to Stata's `marginsplot`:

```{r marginsplot}
library("webuse")
webuse::webuse("nhanes2")
mod3 <- glm(highbp ~ sex * agegrp * bmi, data = nhanes2, family = binomial)
summary(marg3 <- margins(mod3))
plot(marg3)
```

### Conditional effects plots

In addition to the estimation procedures and `plot()` generic, **margins** offers several plotting methods for model objects. First, there is a new generic `cplot()` that displays predictions or marginal effects (from an "lm" or "glm" model) of a variable conditional across values of third variable (or itself). For example, here is a graph of predicted probabilities from a logit model:

```{r cplot1, warning=FALSE}
mod4 <- glm(am ~ wt*drat, data = mtcars, family = binomial)
cplot(mod4, x = "wt", dx = 'drat')
```

And fitted values with a factor independent variable:

```{r cplot2}
cplot(lm(Sepal.Length ~ Species, data = iris))
```

and a graph of the effect of `drat` across levels of `wt`:

```{r cplot3}
cplot(mod4, x = "wt", dx = "drat", what = "effect")
```

### Customizing the look of your plots

Since `cplot()` and `plot()` return `ggplot2` objects, the look is very easy to customize. For example, we could flip the marginal effects plot on its side, change the colors and line type, rename the variables, and add a red line at 0:

```{r plot-look}
library(ggplot2)
mod3 <- glm(highbp ~ sex * agegrp * bmi, data = nhanes2, family = binomial)
marg3 <- margins(mod3)
plot(marg3,
     level = .99,
     colour = 'turquoise', size = 1.5, linetype = 'dashed',
     term_map = c('Body Mass Index' = 'bmi','Gender' = 'sex')) + 
  geom_hline(yintercept = 0, colour = 'red') +
  xlab('The two variables I care about') +
  ylab('Average marginal effects with 95% confidence intervals') +
  coord_flip()
```

Notice that the `agegrp` does not appear in the plot above because it was omitted from the `term_map` argument. This gives you a convenient way to omit terms from the plot.

We can apply the same kinds of changes to graphs produced by `cplot()`:

```{r cplot-look}
library(ggplot2)
cplot(mod4, x = "wt", dx = 'drat', what='effect', size=2, colour='blue', 
      fill = 'pink', alpha=1, linetype='dashed', rugplot=FALSE) + 
    theme_grey() +
    xlab('Custom horizontal label') +
    ylab('Custom vertical label') +
    ggtitle('This is a custom title')
```

You can even use one of many user-created themes that are floating around the web. For instance, here is a plot drawn with the [`ggpomological theme`](https://github.com/gadenbuie/ggpomological) and the [Homemade Apple font](https://fonts.google.com/specimen/Homemade+Apple/):

```{r cplot_pomological, eval = FALSE}
library(ggpomological)
cplot(mod4, x = "wt", dx = 'drat', what='effect', alpha=.5, fill='#efe1c6', colour='#6f5438') + 
    theme_pomological_fancy()
```

If you would like even more control over your plots, `cplot()` can also return a data frame of quantities of interest:

```{r cplot_ggplot2}
dat <- cplot(mod4, x = "wt", dx = "drat", what = "effect", draw = FALSE)
head(dat)
```